---
title: "How to avoid predatory journals and spammy conference invitations?"
author: "Alp Temiz"
date: "`r format(Sys.time())`"
date-format: DD.MM.YYYY - HH:mm - z
format: html
prefer-html: true
editor: visual
editor_options: 
  chunk_output_type: console
fig-format: svg
execute: 
  cache: false
echo: true
message: false
warning: false
error: false
---

```{=html}
<style>
/* Style stdout output blocks */
div.cell-output.cell-output-stdout {
  background-color: #F9F9F9; /* light gray background */
  border: 1px solid #ddd; /* add border */
  padding: 15px; /* add some padding */
  border-radius: 15px; /* rounded corners */
}
</style>
```

```{=html}
<style>
/* Style stdout output blocks with increased specificity */
div.cell-output.cell-output-stdout,
div.cell-output.cell-output-stdout * { /* This targets all children elements as well */
  color: #777777 !important; /* bright pink text color, forced */
}
</style>
```

```{r knitr}
#| echo=FALSE
knitr::opts_chunk$set(error = FALSE, message = FALSE, warning = FALSE)
```




## Are You a Rheumatologist? Got Invited to Present on Nanoparticles in Japan?

If you’ve been in the medical research field long enough, you’ve probably gotten that email. You know the one: “Congratulations! We’re thrilled to invite you to present at the 10th Annual Nanoparticles in Chemistry Symposium in Tokyo!” Now, you’re a rheumatologist whose work has nothing to do with nanoparticles or chemistry. But hey, Tokyo sounds nice! Should you go?

### So… Why the Bizarre Invitations?
Spammy invitations from completely unrelated journals and conferences are all too familiar. Rheumatologists presenting at a nanoparticle symposium, orthopedic surgeons at a virology conference, dentists at a robotics event—the list goes on. Just as ignoring these invitations doesn’t seem to make them stop, neither does marking them as spam. The emails keep coming, from all kinds of different senders and slightly tweaked names. You might find yourself thinking, *Why am I still getting these?*

And occasionally, it’s not a nanoparticle conference in Japan that emails you, but a seemingly relevant rheumatology or immunology journal that *almost* looks legitimate. That’s when things get tricky; these predatory journals are getting more sophisticated, and even experienced researchers fall into their traps.

### The Spam Folder Black Hole (Or Lack Thereof)
With your email address printed on every published article, you’re basically advertising, “Come spam me!” Predatory journals and scammers are lurking, ready to pounce. Even when my university's email system claims to have a spam filter, I still end up with a dozen new offers to present my Psoriatic Arthritis findings at the International Conference of Quantum Dynamics or other questionable “opportunities”. It’s like email whack-a-mole: no matter how many you block, they keep popping up.

### The Perils of the Unsubscribe Button
Let’s talk about the "Unsubscribe" button, which these emails often include. *Do not click it.* I repeat, *do not click that unsubscribe button!* That “unsubscribe” link is usually a one-way ticket to the main train station of the Malware City. Before you know it, your data may be compromised, your research lost, and—if you’re lucky—they only swiped your credit card number. A sobering reality check: falling victim to these scams can put you and your patients at serious risk, especially if they get access to any non-anonymized clinical data.

### Tried Asking IT for Help?
“Oh, IT can handle this!” You might think. I certainly did. But in my experience, even IT seems at a loss when dealing with these relentless spammers. Despite filters, blockers, and firewalls, they just keep coming. This has led me to take matters into my own hands—enter *The Great Domain Block List.*

### The Secret Weapon: Domain Blocking
One thing that does help? Blocking entire domains, not just single emails. Sure, they’ll switch from "tom@predatoryjournal.com" to "rachel@predatoryjournal.com," but if you block “predatoryjournal.com” entirely, you’re one step closer to peace. Now I rarely get these emails in my inbox, as over ten of them get filtered out every half day.

### Want to Join the Fight?
I’ve curated a personal domain blacklist of the worst offenders. Copy-pasting this list into your blocklist might save you a lot of frustration. Let’s join forces! If you send me the domains cluttering your inbox, I’ll happily add them to my list. Maybe one day, we’ll have a comprehensive “Spam Block Bible” for all researchers who just want to work in peace. 

Happy blocking!



```{r}
#| echo=FALSE
library(tidyverse)
library(janitor)
library(openxlsx)
library(skimr)
library(caret)
library(glmnet)
library(pROC)
library(kableExtra)
library(readxl)

library(table1)

library(Matrix)
library(writexl)





```

```{r}
#| eval=FALSE
215825094.mailchimpapp.com
acquaintpublicationsgroup.live
advsurgsci.org
analytical2025-chemistry.com
analytical-chemistry2025.com
analytical-symposium2024.com
analytix-congress2025.com
annalsofcasereports.org
anncaserepimages.info
anncrmijurnl.info
artpublication.org
asjsms.com
austinmedresearch.com
authpubattrib.info
bax1.online
bigmarker.com
bilpublishing.net
biomedgrid.org
biomedgridresearch.org
biomed-res.com
biomed-res.org
biomedresresearch.co
biomedresresearch.com
biomedresresearch.org
blindreveiw.com
bpic-expo2024.com
cancercases.org
cardiologyauctoresonline.com
casesportal.online
casetrials.org
catalysis-congress.com
catalysis-symposium2025.com
cjpu.org
clevermatrix.org
clinicalmedic.com
clinicalnetworks.org
clinicalpapers.org
clinresearchstudies.org
conferenceinvites.org
conferenceprofspeakers.com
conferencesinsight.org
conferencestalkglobal.org
confshare.org
crimsonpublisher.com
cyagenbiosci.com
datadiscoverhub.biz
datadiscoverhub.net
dataexplorerhub.net
dataexplorerhubs.biz
directivepubcations.com
directivepubcations.org
directivepubcltions.org
directivepublication.org
directivpublications.com
directvepubctions.com
directvepubctions.org
eclinicalsci.com
eclinmed.com
editorialboard10@gmail.com
editorialboard37@gmail.com
editorialboardb24@gmail.com
eebioj.org
endocrinologyauctoresonline.com
eurosasiaconferences.com
explorecasespub.com
fjopz.com
food-congress.com
fortuneloa.com
gblscientificguild.org
gcke-congress.top
globalconferencemeet.com
globalindexing.net
globalscientificmeetings.net
globalscientificmeetings.org
gloriamartinremedy6@gmail.com
gresearchhealth.com
gsb2025-scitechcongress.com
gsgforum.com
hrpublicationslv.com
hspcorporation.net
hspcprocess.net
ijcicr.org
ijcmcasereports-us.info
ijcmcasestudy-io.info
ijiset.com
ijowcmc.com
ijseas.com
impactexplorers.org
impactnavigator.biz
indexedjournals.co
indexscript.org
info.wiley.com
inovineconference.com
investigatorspace.com
irispublishers.org
jartificialintelligence.info
jbiomedsci.net
jbresonline.com
jcmiedl.com
jcmimagescasereports.com
jjgahhep.com
jjgastroenterology.info
joddmc.net
joeducation.net
joindeepc.com
jopsci.org
journalssurgery.info
journal-submission.com
j-scimedcentral.us
jscimedpro.com
jscimedsubmissions.com
jsmclinics.com
jsmsubmission.com
jsmsubmissions.org
juniperpublications.org
juniperpublishers.co
lambdaconferences.org
literaryresearch.org
mailer.openpubsphere.com
mailer.opensciencejournals.net
mailguild.info
mcjrnlsschlrsd.info
medcdmo.com
meddocsoajurnalss.org
medicalclinicalcasestudyreports.org
medicineauctores.com
medicinejournalshsoa.org
medischolars.com
medjrnlresearchelicit.com
medloa.com
medoaustinjournals.info
medsresearch.info
meetingsint.net
meetingsnews.com
meghaz-meetings.org
nissipetricia.reviewprocess@gmail.com
openimpactforges.net
openpubspheres.net
openpubspheres.org
opulentmeetings.org
peersciences.com
pepcon2024.com
polscientific.com
pol-scientific.com
precisionglobalcon.org
precisionglobalconferences.org
prowebinarplaner.com
przevents.org
przforum.org
ptechzoa.net
ptechzoa.org
ptzscience.org
pubintellects.com
pubintellects.net
pubknowledgehub.biz
pubknowledgehubs.com
pulsusconferencs.com
rachelwalker32100@gmail.com
resartmetastand.info
rescollabhub.com
resdatacite.info
resdatacollab.info
resdataguides.biz
resdataharbor.net
resdataharvest.org
resdatamethods.info
resdataplus.org
researcher102.com
researchers-forum.com
researchersmeet.com
researchexplore.org
researchfront.biz
researchfrontline.org
researchmatrices.net
researchmatrices.org
researchsynergize.biz
researchvanguards.biz
researchwaves.net
rhadconference.org
rowpapers.com
salientjourhub.com
scholarlinkage.net
scholarlyopenaccessjournals.org
sciarticles.biz
scichemj.org
sciensl.com
scientificresearch.uk
scijour.info
scijournalmedncfp.com
scimedarticles.com
scimedjrnlarchivehub.com
sin-chn.net
smjournalpublications.com
smsubmissions.com
speakersgathering.com
stemjournal.info
submitmanu.com
submitopen.org
submitpaper.info
submitresearchers.com
surgicalcase.info
techsummit25@gmail.com
theconferencemail.org
thetsgcongress.com
tsgcongress.org
ubigene.cn
ubigene.tech
unileon.es
unitedmeetings.co.uk
virtualevent.biz
vyyoma.com
wbickr-conference2024.com
wcdd-symposium.com
wcdwce2025.com
wcfn2024conference.com
wcfn-symposium2025.com
yourcharter.ru
```